Quantum Interval-Valued Probability: Measurement and Probability

### 2017-11-26 prop_iop.tex
prop_iop.tex \subsection{Expectation Values for QIVPMs} Add more reference...

Before discussing QIVPMs, we first review various notations brought
forward from conventional quantum theory. Assume that a physical system
is represented by a density matrix~$\rho$, and that we wish to measure
a physical quantity~${\cal O}$ of this system, with corresponding
observable~$\mathbf{O}$, whose spectral decomposition is given by
\begin{equation}
\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition-distinct}
\end{equation}
where the positive and negative eigenvalues are ordered from the smallest
to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}<\ldots<\lambda_{1}^{-}<0\le\lambda_{1}^{+}<\ldots<\lambda_{N^{+}}^{+}\,,
\end{equation}
and $P_{i}$ is the projector onto the eigenspace of each distinct
eigenvalue~$\lambda_{i}$. This spectral decomposition might be different
from the one people used to~.

>>>>

Before discussing QIVPMs, we first review various notations brought
forward from conventional quantum theory. Assume that a physical system
is represented by a density matrix~$\rho$, and that we wish to measure
a physical quantity~${\cal O}$ of this system, with corresponding
observable~$\mathbf{O}$, whose spectral decomposition is given by~\cite{Griffiths1994,FraleighBeauregard1995,544199,FriedbergInselSpence2002,Jaeger2007}
\begin{equation}
\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition-distinct}
\end{equation}
where the positive and negative eigenvalues are ordered from the smallest
to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}<\ldots<\lambda_{1}^{-}<0\le\lambda_{1}^{+}<\ldots<\lambda_{N^{+}}^{+}\,,
\end{equation}
and $P_{i}$ is the projector onto the eigenspace of each distinct
eigenvalue~$\lambda_{i}$. This spectral decomposition might be different
from the one people used to~.
